---
title: "Ask A Manager 2021"
author: "Group 5 MAM"
date: "2021-09-16"
output: html_document
---

```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE)     # display code as typed
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```

```{r load-libraries, echo=FALSE, warning=FALSE}
library(tidyverse)
library(janitor) 
library(skimr)
library(countrycode) # to clean up country names
library(broom)
library(car)
library(ggfortify)
library(mosaic)
library(dplyr)
library(huxtable)
library(ggthemes)
library(tidyquant)
library(hrbrthemes)
library(viridis)
library(infer)

```


```{r}
# load "Ask a A Manager 2021 Survey" googlesheet
# https://www.askamanager.org/
ask_a_manager_2021 <- read_csv(here::here("data","ask_a_manager.csv"))

skimr::skim(ask_a_manager_2021)

```

# Data cleaning (exchange rate: Alex)

After skimming the dataset, we took the below steps to clean the raw data :

- Removing NA values
- Removing outliers (out of 3$\sigma$)
- Transforming certain datatype into factor
- Selecting key industries from 1000+ industries reported
- Unifying currencies

## Removing NA values

```{r remove-na}
# remove the NA values
ask_a_manager_2021 <- ask_a_manager_2021 %>% 
  filter(!gender %in% c("NA","Other or prefer not to answer","Prefer not to answer", "Non-binary", NA) &
           race!="NA" &
           highest_level_of_education_completed!="NA")
```

## Removing outliers

```{r remove-outliers-z-score}
# using z-score. remove data out of 3 sigma
ask_a_manager_2021 <- ask_a_manager_2021[-which(abs(scale(ask_a_manager_2021$annual_salary))>3),]

```

```{r}
# using quantile. remove data larger than 75%+1.5*IQR or smaller than 25%-1.5*IQR
# Q <- quantile(ask_a_manager_2021$salary, probs=c(.25, .75))
# iqr <- IQR(ask_a_manager_2021$salary)
# up <-  Q[2]+1.5*iqr # Upper Range  
# up <-  Q[1]-1.5*iqr # Upper Range  
# ask_a_manager_2021 <- ask_a_manager_2021 %>% 
#   filter(salary>=low & salary<=up)
```

## Transforming into ordered `factor` datatype

Namely, we want to make age, years of working experience, education into `factor`, and take the log of salary for the next step of EDA.

```{r, warning=FALSE}
ask_a_manager_2021 <- ask_a_manager_2021 %>% 
  mutate(
    country = countrycode::countryname(country),
    age_group = factor(how_old_are_you,levels=c("under 18","18-24","25-34","35-44","45-54","55-64","65 or over")),
    field_exp = factor(years_of_experience_in_field,levels=c("1 year or less","2 - 4 years","5-7 years","8 - 10 years","11 - 20 years","21 - 30 years","31 - 40 years","41 years or more")),
    pro_exp = factor(overall_years_of_professional_experience,levels=c("1 year or less","2 - 4 years","5-7 years","8 - 10 years","11 - 20 years","21 - 30 years","31 - 40 years","41 years or more")),
    education = factor(highest_level_of_education_completed, labels=c("High School","Some college","College degree","Master's degree","Professional degree", "PhD")),
    higher_edu = ifelse(education %in% c("College degree","Master's degree", "PhD", "Professional degree"),1,0),
    salary = annual_salary,
    log_salary = log(annual_salary)
  ) %>% 
  janitor::clean_names() # clean columns names
```

## Selecting industries

Since there are over 1000 reported industries in the dataset, we will only keep the top 25 industries which account for 92% of total entries

```{r select top industry, warning=FALSE}
# Industry is messy... it has > 1000 different industries.
# we only keep the names of top 25 industries. (24597(92%) out of 26765 entries)
industry_list <- ask_a_manager_2021 %>% 
  count(industry, sort=TRUE) %>% 
  mutate(percent = 100* n/sum(n)) %>% 
  slice_max(order_by = n, n = 25) %>% 
  select(industry)

ask_a_manager_2021 <- ask_a_manager_2021 %>% 
  mutate(industry = ifelse(industry %in% industry_list$industry,
                           industry,
                           "Others"))

```

## Unifying currencies

Since there are 11 different currencies reported in the dataset, we want to unify the most common currencies into USD for the convenience of comparison analysis afterwards. We decided to convert all currencies with occurences greater than 100 into USD. This included CAD,GBP,EUR,AUD/NZD. Other was not converted as there wasn't specific information on the currency.

```{r}
ask_a_manager_2021 %>%
  count(currency, sort=TRUE) %>%
  mutate(percent = 100* n/sum(n))

```

From the above table, We can see that USD, CAD, GBP, EUR, (AUD/NZD) are the most common currencies. We will convert the currencies all to USD using exchange rate data from library `quantmod`, and the exchange rate will be taken from the last date of the survey "2021-09-14"

```{r warning=FALSE, message=FALSE}
library(quantmod)
#library to get currency data (and other financial data)

#gets the currency rate for the currency pairs. This uses the Oanda which keeps currency data for the last 180 days.
#In 180 days from "2021-09-14" the code will no longer return the currency rates.
currencies <-getSymbols(c("EUR/USD","CAD/USD","GBP/USD","AUD/USD" , "NZD/USD"),
                        from="2021-09-14", to="2021-09-14", src="oanda")

#In order to preserve the analysis for after 180 days we can hard code the currency rates into a tibble
currencies_preserved <- tibble(
  name = c("EUR/USD","CAD/USD","GBP/USD","AUD/USD" , "NZD/USD"),
  value = c(1.18,0.79,1.38,0.734,0.711)
)

```

Here we create a new column called `converted_salary` which converts the 5 most common currencies in USD. These are then rounded to the nearest whole number. 
```{r}
#the values are taken from the currencies_preserved$value as to preserve the analysis when 
# getSymbols will no longer work. The index matches the currency pair.
ask_a_manager_2021 <- ask_a_manager_2021 %>% 
  mutate(converted_salary = case_when(
    currency == "GBP" ~ round(annual_salary*currencies_preserved$value[3]),
    currency == "AUD/NZD" & country == "Australia" ~ round(annual_salary*currencies_preserved$value[4]),
    currency == "AUD/NZD" & country == "New Zealand" ~ round(annual_salary*currencies_preserved$value[5]),
    currency == "CAD" ~ round(annual_salary*currencies_preserved$value[2]),
    currency == "EUR" ~ round(annual_salary*currencies_preserved$value[1]),
    TRUE ~ round(annual_salary)
  ))

```

```{r}
#Here we filter the dataset to only include the salaries that were converted into USD terms. The other currencies also included lots of outliers which we also get rid of here.

ask_a_manager_2021 <- ask_a_manager_2021 %>% 
  filter(currency %in% c("USD","GBP","AUD/NZD","EUR","CAD") &
           !is.na(country))

ask_a_manager_2021 %>%
  count(currency, sort=TRUE) %>%
  mutate(percent = 100* n/sum(n))
```

# Exploratory Data Analysis

## Counts

```{r, fig.width=3}
# Some quick counts, groups, etc
ask_a_manager_2021 %>% 
  count(age_group, sort=TRUE) %>% 
  mutate(percent = 100* n/sum(n)) %>% 
  ggplot(aes(x=fct_relevel(age_group,levels=c("under 18","18-24","25-34","35-44","45-54","55-64","65 or over")), y=n)) +
  geom_bar(stat="identity") + labs(title = "Age distribution of Ask a Manager survey respondents",                                                 x="Age group",
                  y="Frequency",                                                  caption = "Source:Askamanager.com")

# 'country' 
ask_a_manager_2021 %>%
  count(country, sort=TRUE) %>% 
  mutate(percent = 100* n/sum(n))

# 'city' 
ask_a_manager_2021 %>% 
  count(city, sort=TRUE) %>% 
  mutate(percent = 100* n/sum(n))

# education 
ask_a_manager_2021 %>% 
  count(education) %>% 
  mutate(percent = 100* n/sum(n))%>% 
  arrange(desc(percent))

# gender
ask_a_manager_2021 %>% 
  count(gender) %>% 
  mutate(percent = 100* n/sum(n))%>% 
  arrange(desc(percent))

# race
ask_a_manager_2021 %>% 
  count(race) %>% 
  mutate(percent = 100* n/sum(n))%>% 
  arrange(desc(percent))

# pro_exp 
ask_a_manager_2021 %>% 
  count(pro_exp ) %>% 
  mutate(percent = 100* n/sum(n))%>% 
  arrange(desc(percent))

# field_exp  
ask_a_manager_2021 %>% 
  count(field_exp  ) %>% 
  mutate(percent = 100* n/sum(n))%>% 
  arrange(desc(percent))

```

## Salary (Yuan)

How is salary distributed?

```{r}

favstats(ask_a_manager_2021$salary) # find a really rich guy here

# density
g1 <- ggplot(ask_a_manager_2021, aes(x=salary))+
  geom_density()+
  NULL
#cdf
g2 <- ask_a_manager_2021 %>% 
  slice_min(order_by = salary,n =nrow(ask_a_manager_2021)-5) %>% # choose a number
  ggplot(aes(x=salary))+
  stat_ecdf()+
  NULL

# taking log is better
g3 <- ggplot(ask_a_manager_2021, aes(x=log(salary)))+
  geom_density()+
  NULL

g4 <- ask_a_manager_2021 %>% 
  slice_min(order_by = salary,n =nrow(ask_a_manager_2021)-5) %>% # choose a number
  ggplot(aes(x=log(salary)))+
  stat_ecdf()+
  NULL

gridExtra::grid.arrange(g1,g2,g3,g4)
```

Observation: This is a right skewed distribution. 

## Industry (Yuan)

```{r}
ask_a_manager_2021 %>% 
  count(industry, sort=TRUE) %>% 
  ggplot(aes(y=fct_reorder(industry,n), x=n))+
  geom_col()

```

Observations:

- Computing & tech is the top-chosen industry among respondents, followed by Education and Non-profit
- This indicate that the sample might include more respondents from industries have higher exposure to tech and internet.

## Salary ,Gender and Industry (Yuan)

We are interested in the type of industries with top salary for man and woman.

```{r, fig.width=5}
# Industries of top average salary for Man and Woman
salary_table <- ask_a_manager_2021 %>% 
  group_by(industry, gender) %>% 
  summarise(count = n(),
            avg_salary = mean(converted_salary),
            higher_edu_prop = sum(higher_edu)/n()) %>% 
  pivot_wider(id_cols = 1:5,
              names_from = gender,
              values_from = count:higher_edu_prop)
  
g_man <- salary_table %>% 
  ggplot(aes(y=fct_reorder(industry,avg_salary_Man), x=avg_salary_Man,fill=higher_edu_prop_Man))+
  geom_bar(position="dodge", stat="identity")+
  geom_text(aes(label=paste(avg_salary_Man%/%1000,"k")),
            position=position_dodge(width=0.9), hjust=0,vjust=0)+
  scale_x_continuous(labels = scales::comma) +
  scale_fill_gradient(low="sky blue", high="blue")+
  labs(
    title="Man",
    x="Annual Salary $",
    y="Industry",
    fill="Higher Education %"
  )+
  theme_wsj()+
  theme(legend.position="bottom",
        legend.title=element_text(size=13))+
  NULL

ggsave("highest_paid_industries_male.png",width = 12,height = 8,limitsize = F)
g_woman <- salary_table %>% 
  ggplot(aes(y=fct_reorder(industry,avg_salary_Woman), x=avg_salary_Woman,fill=higher_edu_prop_Woman))+
  geom_bar( position="dodge", stat="identity")+
  geom_text(aes(label=paste(avg_salary_Woman%/%1000,"k")),
              position=position_dodge(width=0.9), hjust=0,vjust=0)+
  scale_x_continuous(labels = scales::comma) +
  scale_fill_gradient(low="pink", high="red")+
  labs(
    title="Woman",
    x="Annual Salary $",
    y="Industry",
    fill="Higher Education %"
  )+
  theme_wsj()+
  theme(legend.position="bottom",
        legend.title=element_text(size=13))+
  NULL


ggsave("highest_paid_industries_female.png",width = 12,height = 8,limitsize = F)

```

Observations:

- For both man and woman, the top earning industries are alike (Law, Computing or Tech, Business or Consulting)
- Respondents from Law, Govenment and Education tends to have higher education level compared to the rest, reflecting the academic/professional requirements of these positions
- The difference between the salary within sales and accounting, banking & finance is likely due to the subdivisions chosen based on gender nature

We are also interested in the salary difference between man and woman within the same industry.

```{r salary_gap_by_industry}
# salary gap in different industries
ask_a_manager_2021 %>% 
  group_by(industry, gender) %>% 
  summarise(count = n(),
            avg_salary = mean(converted_salary)) %>% 
  pivot_wider(id_cols = 1:4,
              names_from = gender,
              values_from = count:avg_salary) %>% 
  mutate(size = count_Man+count_Woman,
         male_prop = count_Man/(count_Man+count_Woman),
         salary_gap = avg_salary_Man - avg_salary_Woman) %>% 
  ggplot(aes(y=fct_reorder(industry,salary_gap), x=salary_gap,fill=male_prop))+
  geom_col()+
  
  # geom_point(aes(y=fct_reorder(industry,size),x=size*10))+
  
  scale_x_continuous(
    breaks = seq(-20000,40000,5000)
  ) +
  scale_fill_gradient(low="pink", high="blue")+
  labs(
    title="Salary Gap and Sex Ratio",
    x="Salary Gap in $",
    y="",
    fill="Male %"
  )+
  theme_wsj()+
  theme(legend.position="bottom",
        legend.title=element_text(size=13))+
  NULL

ggsave("salary_gap.png",width = 12,height = 8,limitsize = F)

```

Observations:

- Man has a higher average salary than woman in most of the industries, with Law being the most significant
- Woman has higher average salary in Art & Design
- The proportion of male within computing or tech is significantly higher than that within other industries; yet the proportion only reaches c. 40%, reflecting the fact that most respondents are female because Ask_a_manager is more popular among women
- The proportion of male is also higher in labour-intensive industries such as transport or logistics, engineering, utilities & telecommunications

## Education (Jean)

Next, we want to see if there is a difference in the salary gap between man and woman for different education level.

```{r salary_gap_by_education}
ask_a_manager_2021 %>% 
  group_by(education, gender) %>% 
  summarise(count = n(),
            avg_salary = mean(converted_salary)) %>% 
  pivot_wider(id_cols = 1:4,
              names_from = gender,
              values_from = count:avg_salary) %>% 
  mutate(size = count_Man+count_Woman,
         male_prop = count_Man/(count_Man+count_Woman),
         salary_gap = avg_salary_Man - avg_salary_Woman) %>% 
  ggplot(aes(x=education, y=salary_gap,fill=male_prop))+
  geom_col()+
  scale_y_continuous(
    breaks = seq(-20000,40000,5000)
  ) +
  scale_fill_gradient(low="pink", high="sky blue")+
  theme_wsj()+
  theme(legend.position="bottom", axis.title=element_text(size=24))+
  ggtitle("Salary Gap at Different Education level") +
  xlab("Education Level") + ylab ("Salary Gap Between Man and Woman in $") + 
  NULL


```


```{r Education_salary, warning=FALSE, echo=FALSE}

ask_a_manager_2021 %>% 
  filter(gender %in% c("Man", "Woman")) %>% 
  mutate(sex = factor (gender, labels = c("Man", "Woman"))) %>% 
  rename(Education = education) %>% 
  group_by(Education, gender) %>% 
  summarise (median_salary_by_edu = median (converted_salary),
             mean_salary_by_edu = mean(converted_salary), ) %>% 
  ggplot () +
  geom_col(aes (Education, median_salary_by_edu, fill = gender), position = position_dodge(width = 0.9), alpha = 0.7)+
#Removed the section which broke the code
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  NULL


```


## Race (Clara)

### Count 
```{r}
ask_a_manager_2021 %>% 
  group_by(race) %>% 
  filter(n() > 500) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(y=count, x=race, fill=race))+
  geom_col() +
  theme_wsj()+
  theme(legend.position = "none") +
  labs(x="Race", y="Count", title="Count by Race", subtitle = "Races with > 500 Respondents")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + 
  NULL
```


### Race and Mean Salary 

```{r}
ask_a_manager_2021 %>% 
  filter(industry %in% industry_list$industry) %>% 
  group_by(race) %>% 
  filter(n() > 500) %>% 
 ggplot( aes(x=race, y=converted_salary, color=race)) +
    geom_jitter(color="black", size=0.01, alpha=0.9) +
   geom_boxplot(alpha=0.4) +
   scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    geom_hline(yintercept=144988, color="red") +
    theme_wsj() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    theme(axis.title=element_text(size=12))+
    ggtitle("Salary Vs. Race Boxplot with Jitter") +
    ylab("Salary") + xlab ("Race") + 
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
    scale_y_continuous(labels = scales::comma) +
    NULL
  
```
Observation:
In our boxplot one can visualize both the distribution of the data and the medium and interquartile ranges of the data. When comparing annual salary by race, our data shows that Asians have the higher salaries in comparison to Black and African American and White sample respondents. Interestingly enough, our sample also shows that the medium salary for Black and AA respondents is higher than that of White respondents. 

Since most repondents were white, the larger sample size is less prone to skewness due to outliers when comparing it to the other two races portrayed in the plot. 

```{r}

ask_a_manager_2021_race <- ask_a_manager_2021 %>%
  group_by(race) %>% 
  filter(race %in% c("Black or African American", "White")) 

t.test(salary ~ race, data = ask_a_manager_2021_race)

```
When running a T-test on the two racial groups, White and Black or African American, the P-value we get is 0.9. Thus there is no statistically signifcant difference in their annual salary when calculating it based of off this data set. 
### Race and Mean Salary 

```{r}
# Remove from presentation
ask_a_manager_2021 %>% 
  group_by(race) %>% 
  filter(n() > 500) %>% 
  ggplot(aes(y = log(converted_salary), x=race))+
  geom_boxplot() +
  theme_bw()+
  theme(legend.position = "none")+
  labs(title = "Distribution of Annual Salaries by Racial Group",
       x = "Race",
       y = " ")+
  NULL
```

```{r}

```

## Location (Alex)

```{r}
#This package is useful for creating a map of the USA
library(usmap)
library(ggrepel)

#create df of the list of states with >10 occurrences 
#This allows us to get data for actual states as many data entry errors
#many individuals put multiple states and this helps to fix that
states <- ask_a_manager_2021 %>% 
  group_by(state) %>%
  filter(!is.na(state)) %>%
  filter(n()>10) %>% 
  summarise(mean_salary = mean(salary),
            count_state = count(state))

states$fips <- fips(states$state)
statesalarymap <- states %>% select(state,mean_salary)

plot_usmap(data=statesalarymap, values="mean_salary", color="black") + scale_fill_continuous(
    low = "white",
    high = "light green",
    name = "Mean Salary") +
  theme(legend.position = "right") +
  labs(title="Map of US States based on Average Salary")


```

> MAP

```{r}
# Count by Industry

ask_a_manager_2021 %>% 
  group_by(industry) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(y=fct_reorder(industry,count),x=count))+
  geom_col()

# null hypothesis: no difference between
```

## Age (Raina)

```{r}
ask_a_manager_2021 %>% 
  group_by(age_group, gender) %>% 
  summarise(count=n()) 
  #ggplot(aes(y=fct_reorder(how_old_are_you,count),x=count))+
  #geom_col()
```



```{r}
# Count by Age Group
ask_a_manager_2021 %>% 
  group_by(age_group,gender) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(y=fct_reorder(age_group,count),x=count))+
  geom_col()+
  scale_fill_gradient(low="pink", high="sky blue")+
  theme_wsj()+
  NULL
# Sorting out the people who are 18+ 
ask_a_manager_age <- ask_a_manager_2021 %>%  
                    mutate(factor(age_group,levels=c("18-24","25-34","35-44","45-54","55-64","65 or over")))
     
```
```{r}
#need to change colors for male and female ?!
#there are only 6 women in under 18 category so excluding them for the graph
# since there is no male data in that category to compare
ask_a_manager_age %>% 
  filter(age_group %in% c("18-24", "25-34" , "35-44" , "45-54" , "55-64"  )) %>% 
  group_by(age_group, gender) %>% 
  summarise (median_salary_by_age = median (converted_salary),
             mean_salary_by_age = mean(converted_salary)) %>% 
  ggplot () +
  geom_col(aes (age_group, median_salary_by_age, fill = gender), position = position_dodge(width = 0.9), alpha = 0.7)+
 # geom_point(aes(x = age_group, y=mean_salary_by_age, color = gender))+
  #geom_point( aes(age_group,mean_salary_by_age,group=1), color="light blue", size=2) +
  theme_wsj()+
  scale_fill_manual(values = c("sky blue", "pink")) +
  theme(legend.position="bottom", axis.title=element_text(size=24))+
  scale_y_continuous(labels = scales::comma) +
  # geom_smooth(aes(x=age_group,y=mean_salary_by_age, colour="black"),se=F,span = 0.2)+ 
  labs(  y="Salary" ,x = "Age Group") +
  #geom_line(aes( x = age_group, y=mean_salary_by_age, gender="Male"  ),colour="blue",size=2)
  NULL
```

# Statistical Tests


## Gender vs Salary (Clara)

### General Statistics & Boxplot

```{r}
mosaic::favstats (converted_salary ~ gender, data=ask_a_manager_2021)

```

```{r}

ask_a_manager_2021 %>% 
  ggplot( aes(x=gender, y=converted_salary, color=gender)) +
    geom_jitter(color="black", size=0.4, alpha=0.9) +
    geom_boxplot(alpha=0.3) +
    scale_fill_viridis(discrete = TRUE, alpha=0.6) +
    theme_wsj() +
    theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
   theme(
      legend.position="none",
      plot.title = element_text(size=11)
    ) +
    theme(axis.title=element_text(size=12))+
    ggtitle("Salary Vs. Gender Boxplot with Jitter") +
    ylab("Salary") + xlab ("Race") + 
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
    scale_y_continuous(labels = scales::comma) +
    NULL
  
```

***For our following analysis, we will be comparing data from the male gender "Man" with data from the female gender "Woman." We will filter out the data on those that are non binary.***

### T-Test

```{r, t_test_for_gender_salary} }

ask_a_manager_2021 <- ask_a_manager_2021 %>%
  filter(gender!="Non-binary")
t.test(converted_salary ~ gender, data = ask_a_manager_2021)
```

### Confidence Intervals 

```{r, gender vs. salary confidence intervals}
 
#mosaic::favstats (annual_salary ~ gender, data=ask_a_manager_2021)
ask_a_manager_2021_gender <- ask_a_manager_2021 %>%
  mutate(gender2 = case_when(
  gender  == "Man" ~ "1",
 gender == "Woman" ~ "0",
  TRUE ~ "NA"
)) %>%
  mutate(gender2 = as.numeric(gender2))


mosaic::favstats (converted_salary ~ gender, data=ask_a_manager_2021_gender) %>%
mutate(t_critical = qt(0.975,n-1),
         sd_mean = sd/sqrt(n),
         margin_of_error = t_critical*sd_mean,
         ci_lower = mean-margin_of_error,
         ci_higher = mean+margin_of_error)
# Add graph of two distributions and confidence intervals 
```

Observation: Since two 95% confidence intervals do not overlap, we are at least 95% confident that the male have higher salary than the female on average.

### Bootstrap Test 

```{r}
# hypothesis testing using infer package
diff <- ask_a_manager_2021_gender %>%
  specify(converted_salary ~ gender) %>%
  calculate(stat = "diff in means", order = c("Woman", "Man"))

set.seed(1234)
salary_in_null_world <- ask_a_manager_2021_gender %>%
  filter(gender !="Non-binary") %>%
  specify(converted_salary ~ gender) %>%
   # assuming independence of gender and salary
  hypothesize(null = "independence") %>%
   # generate 1000 reps, of type "permute"
  generate(reps = 1000, type = "permute") %>%
  # calculate statistic of difference, namely "diff in means"
   calculate(stat = "diff in means", order = c("Woman", "Man")) 

salary_in_null_world %>% 
  visualise()+
  shade_p_value(obs_stat = diff, direction = "two-sided")
  
p_value <- salary_in_null_world %>% 
  get_pvalue(obs_stat = diff, direction="both")
p_value
```
Observation: Our null hypothesis is that the difference of annual salaries between male and female is 0 and we get a p_value very close to 0. Therefore we reject the null hypothesis with 95% confidence. There is difference between the average male and female salary.


## Gender vs Education (Jean)

We want to look at the relationship between one's gender and education degree. In essence, we want to explore if there is a difference in the proportion of respondents with high school degree as their highest degree for male group and the female group. We can use the proportion test to generate the result from the male and female sample.

```{r prop_test_for_gender_education_college}

ask_a_manager_2021_education <- ask_a_manager_2021 %>% 
   filter(gender !="Non-binary") %>%
   mutate(high_school = if_else(highest_level_of_education_completed == "High School", "Yes", "No")) %>% 
   group_by(gender) %>% 
   summarise(college_below=sum(high_school == "Yes"), college_or_above = sum(high_school == "No"))

ask_a_manager_2021_education

prop.test(x = c(4612,20197), n = c(4612+209,20197+339), alternative = "two.sided")


```

From the result of proportion test for male group and female group, we are 99% confident that the proportion of high school as highest education level for male is higher than that for female, indicating that overall female has a higher college-entry rate vs. the male.

If we repeat the process to explore the difference in proportion in acquiring a masters or above degree for both gender:

```{r prop_test_for_gender_education_master}
ask_a_manager_2021_education <- ask_a_manager_2021 %>% 
  filter(gender !="Non-binary") %>%
  mutate(higher_edu = if_else(highest_level_of_education_completed %in% c("Master's degree", "Professional degree", "Phd"), "Yes", "No")) %>% 
  group_by(gender) %>% 
  summarise(master_or_above=sum(higher_edu == "Yes"), master_below = sum(higher_edu == "No"))


ask_a_manager_2021_education

prop.test(x = c(3559,13603), n = c(1262+3559,6933+13603), alternative = "two.sided")
```

From the result of two proportion tests, we can see that even though the proportion of acquiring a college-or-above degree is less in the male group, the proportion of acquiring higher education degree (Master's-or-above) is higher than the female group. This somehow explains the fact that there are more outliers in male sample with extremely high income level.

## Race vs Salary (Raina)

Here we want to see if race is affecting the salary.

```{r t_test_for_race_education}
ask_a_manager_salary <- ask_a_manager_2021 %>% 
  mutate(if_white = if_else(race == "White", "Yes", "No")) %>% 
  select(if_white,salary)
ask_a_manager_salary
t.test(salary~if_white, data = ask_a_manager_salary, success = "Yes")
```

> wisely choose the race. like white vs. not white

## Race vs Education (Jean)

We want to look at the relationship between one's race and education degree. Particularly, we want to see if there is a difference in education level for those being white and those being non-white.

As the above analysis for gender vs. education, we run two proportion tests for college-or-above degree percentage and master-or-above percentage between the male and female group.

```{r prop_test_for_race_education_college}

ask_a_manager_2021_race <- ask_a_manager_2021 %>% 
  mutate(if_white = if_else(race == "White", "White", "Non-white"),
         high_school = if_else(highest_level_of_education_completed == "High School", "Yes", "No")) %>% 
  group_by(if_white) %>% 
  summarise(college_below=sum(high_school == "Yes"), college_or_above = sum(high_school == "No"))

ask_a_manager_2021_race

prop.test(x = c(3893,20916), n = c(80+3893,468+20916), alternative = "two.sided")
```

Similarly, if we run the test for the propotion of master_or_above education level between white and non-white races:

```{r prop_test_for_race_education_master}
ask_a_manager_2021_race <- ask_a_manager_2021 %>% 
  mutate(if_white = if_else(race == "White", "White", "Non-white"),
         higher_edu = if_else(highest_level_of_education_completed %in% c("Master's degree", "Professional degree", "Phd"), "Yes", "No")) %>% 
  group_by(if_white) %>% 
  summarise(master_or_above=sum(higher_edu == "Yes"), master_below = sum(higher_edu == "No"))

ask_a_manager_2021_race

prop.test(x = c(2792,14370), n = c(1181+2792,7014+14370), alternative = "two.sided")
```

From the result of the proportion test, we cannot see a clear difference between the proportion of education level in white and non-white group, as the p-value is higher than 5%.


## Changed Industry? vs salary (Raghav)
```{r}
ask_a_manager_2021_changed <- ask_a_manager_2021  %>%
mutate(if_changed= if_else(overall_years_of_professional_experience == years_of_experience_in_field, "No", "Yes"))

```


```{r}
ask_a_manager_2021_changed %>% 
ggplot(aes(x=fct_relevel(overall_years_of_professional_experience,levels=c("1 year or less","2 - 4 years","5-7 years","8 - 10 years","11 - 20 years","21 - 30 years","31 - 40 years","41 years or more")), y=annual_salary, color=if_changed))+
  # scatter plot
  geom_point(alpha = 0.5)+
  # linear smooth line
  geom_smooth(method = "lm")+
  # legend settings
  theme(legend.position = "bottom",
        legend.title = element_blank())+
  labs(title="Whether changing job affects your salary",
       x="Total Years Spent Working",
       y="Salary")+
  theme_bw()+
  NULL
```


```{r}
ask_a_manager_2021_changed %>% 
  group_by(overall_years_of_professional_experience, if_changed) %>% 
  summarise (median_salary_over_time = median (salary),
             mean_salary_over_time = mean(salary)) %>% 
  ggplot () +
  geom_col(aes (fct_relevel(overall_years_of_professional_experience,levels=c("1 year or less","2 - 4 years","5-7 years","8 - 10 years","11 - 20 years","21 - 30 years","31 - 40 years","41 years or more")), median_salary_over_time, fill=if_changed), position = position_dodge(width = 0.9), alpha = 0.7)+
  geom_point(aes(x = overall_years_of_professional_experience, y=mean_salary_over_time, color = if_changed))+
  theme_bw()+
  #formatC(x, format = "d")+
  labs(  title =  "Median Salary over time" , y="Salary" ,x = "Prof") +
  NULL
```


```{r}
t.test(salary~if_changed, data = ask_a_manager_2021_changed)


prop.test(~if_changed, data = ask_a_manager_2021_changed, success = "Yes")
ask_a_manager_age %>% 
  filter(age_group %in% c("18-24", "25-34" , "35-44" , "45-54" , "55-64"  )) %>% 
  group_by(age_group, gender) %>% 
  summarise (median_salary_by_age = median (salary),
             mean_salary_by_age = mean(salary)) %>% 
  ggplot () +
  geom_col(aes (age_group, median_salary_by_age, fill = gender), position = position_dodge(width = 0.9), alpha = 0.7)+
  geom_point(aes(x = age_group, y=mean_salary_by_age, color = gender))+
  theme_bw()+
  #formatC(x, format = "d")+
  labs(  title =  "Median Salary by Age Group" , y="Salary" ,x = "Age Group") +
  NULL
```


# Regression Analysis (Yuan)

```{r}
colnames(ask_a_manager_2021)
```


```{r}
reg_data <- ask_a_manager_2021 %>% 
  mutate(country = ifelse(country=="US","US","Non-US"))

m1 <- lm(converted_salary ~ education, data=reg_data)
m2 <- lm(converted_salary ~ education + age_group, data=reg_data)
m3 <- lm(converted_salary ~ education + gender, data=reg_data)
m4 <- lm(converted_salary ~ education + age_group + gender + pro_exp + field_exp, data=reg_data)
m5 <- lm(converted_salary ~ education + age_group + gender + field_exp, data=reg_data)

huxreg(m1, m2, m3, m4, m5,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')

```


